Comunicações Hiperligadas: Novo Paradigma de Comunicação e Colaboração, potenciado pela Tecnologia WebRTC

### 2015-05-26 tese/arch01.tex
[ADD] final structure, ignore portuguese

@@

Although the core infrastructure is important and crucial for the implementation of our web application, there is no preference for a specific software running on the web server. An important requirement for the Web Server is the WebSockets support, LAMP server was considered, although the chosen technology for web development is Play Framework with Java, which has a more evident separation between Model, View and Controller components.

For the signaling server there is also no preference between \ac{SIP} and \ac{XMPP}, as both support presence information feature. SigOFly could be adopted as well but using it would be irrelevant for the final result of this project. For sake of simplicity and easy deployment the chosen platform chosen is the Openfire \ac{XMPP} server.

The streaming server will be without any doubt \emph{Jitsi Videobridge} as \emph{Jitsi} team is working with \ac{WebRTC} and their code is open source.

@@

@@

>>>>

\subsection{Infrastructure}

@@

Although the core infrastructure is important and crucial for the implementation of our web application, there is no preference for a specific software running on the web server. An important requirement for the Web Server is the WebSockets support, \emph{LAMP} server was considered, although the chosen technology for web development is \emph{Play Framework} with \emph{Java}, which has a more evident separation between \emph{Model}, \emph{View} and \emph{Controller} components.

For the signaling server there is also no preference between \ac{SIP} and \ac{XMPP}, as both support presence information feature. \ac{SigOfly} could be adopted as well but using it would be irrelevant for the final result of this project. For sake of simplicity and easy deployment the chosen platform chosen is the \emph{Ejabberd} \ac{XMPP} application server since it implements \cite{xep0206} which is crucial for web applications, \emph{Ejabberd}, as said before, is also the \ac{XMPP} server that implements more extensions. For simplicity, \emph{Ejabberd} will be configured as a single node instead a member of cluster.

The streaming server will be \emph{Jitsi Videobridge} as \emph{Jitsi} team is working with \ac{WebRTC} and their code is open source.

@@

\subsection{Software}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.95\textwidth]{figures/apparch.png}
	\caption{App Architecture}
\end{figure}

### 2015-05-26 tese/project.tex
added more bibliography
interactive RTP
14 pages, DTLS, TLS, SRTP, SCTP
english syntax for section 1, webrtc stack figure
added references, almost concluding syntax checking for section 3
done syntax review, I may talk about sig-o-fly and identity stuff
added sig-o-fly, a little bit running
removed overfull hbox
[ADD] added more on Wave, I must talk about goodow and jupiter
[ADD] goodow, [START] architecture
[ADD] final structure, ignore portuguese

\documentclass{llncs}
\RequirePackage[english]{babel} % Se fizerem o texto em ingles
\usepackage[english]{babel}   
\usepackage[latin1]{inputenc}
%\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}

\usepackage[fleqn]{amsmath}
\usepackage{amssymb}
\usepackage{makeidx}  % allows for indexgeneration
\usepackage{graphicx}  % allows for indexgeneration
\usepackage{subfig}  % allows for indexgeneration
\usepackage{color}  % allows for indexgeneration
\usepackage{url}
\usepackage{hyperref}

\usepackage{acronym}
\newacro{API}{Application Programming Interface}
\newacro{BOSH}{Bidirectional-streams Over Synchronous HTTP}
\newacro{CSS}{Cascading Style Sheets}
\newacro{CPU}{Central Processing Unit}
\newacro{CRUD}{Create, Read, Update and Delete}
\newacro{DOM}{Document Object Model}
\newacro{DTLS}{Datagram Transport Layer Security}
\newacro{FMS}{Flash Media Server}
\newacro{HTML}{HyperText Markup Language}
\newacro{HTTP}{Hypertext Transfer Protocol}
\newacro{ICE}{Interactive Connectivity Establishment}
\newacro{IPv4}{Internet Protocol Version 4}
\newacro{IPv6}{Internet Protocol Version 6}
\newacro{IP}{Internet Protocol}
\newacro{MPEG}{Moving Picture Experts Group}
\newacro{NAT}{Network Address Translation}
\newacro{P2P}{Peer-to-peer}
\newacro{PSTN}{Public Switched Telephone Network}
\newacro{RTMP}{Real Time Messaging Protocol}
\newacro{RTMFP}{Real-Time Media Flow Protocol}
\newacro{RFC}{Request For Comments}
\newacro{SAMI}{Synchronized Accessible Media Interchange}
\newacro{SCTP}{Stream Control Transmission Protocol}
\newacro{SRTP}{Secure Real-time Transport Protocol}
\newacro{SDP}{Session Description Protocol}
\newacro{SIP}{Session Initiation Protocol}
\newacro{SIMPLE}{SIP for Instant Messaging and Presence Leveraging Extensions}
\newacro{SMIL}{Synchronized Multimedia Integration Language}
\newacro{SMS}{Short Message Service}
\newacro{SRT}{SubRip Text}
\newacro{STUN}{Session Traversal Utilities for NAT}
\newacro{SVG}{Scalable Vector Graphics}
\newacro{TCP}{Transmission Control Protocol}
\newacro{TLS}{Transport Layer Security}
\newacro{TMN}{This Means Nothing}
\newacro{TURN}{Traversal Using Relays around NAT}
\newacro{UDP}{User Datagram Protocol}
\newacro{VoIP}{Voice Over IP}
\newacro{WebRTC}{Web Real-Time Communication}
\newacro{WebVTT}{Web Video Text Tracks}
\newacro{XAML}{eXtensible Application Markup Language}
\newacro{XEP}{XMPP Extensions}
\newacro{XML}{eXtensible Markup Language}
\newacro{XMPP}{Extensible Messaging and Presence Protocol}
\newacro{XHTML}{eXtensible Hypertext Markup Language}
\overfullrule=2cm

@@

\begin{abstract}
    In here put your abstract. Sed ut perspiciatis unde omnis iste natus error sit voluptatem accusantium doloremque laudantium, totam rem aperiam, eaque ipsa quae ab illo inventore veritatis et quasi architecto beatae vitae dicta sunt explicabo. Nemo enim ipsam voluptatem quia voluptas sit aspernatur aut odit aut fugit, sed quia consequuntur magni dolores eos qui ratione voluptatem sequi nesciunt. Neque porro quisquam est, qui dolorem ipsum quia dolor sit amet, consectetur, adipisci velit, sed quia non numquam eius modi tempora incidunt ut labore et dolore magnam aliquam quaerat voluptatem. 
\keywords{keyworkd1, keyworkd2, keyworkd3}
\end{abstract}

\section{Introduction}
  \input{section01.tex}
\section{\color{red}Signaling}
  \input{section02.tex}
\section{\color{red}Hypermedia}
  \input{section03.tex}
\section{\color{red}Applications}
  \input{section04.tex}

\subsection{Context}   % English
\subsection{Problem Statement / Solution Statement} % English
\subsection{Thesis Contributions} % English
\subsection{Article Structure} % English
% \section{Proposed Architecture} % English
\subsection{Methodology} % Section
\subsection{Planned Schedule} % English
\section{Conclusions} % English
\subsection{Summary} % English
\section{Conclusions} % English
\bibliographystyle{splncs03}
\bibliography{references}

>>>>

\documentclass{llncs}
\RequirePackage[english]{babel} % Se fizerem o texto em ingles
\usepackage[english]{babel}   
%\usepackage[latin1]{inputenc}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}

\usepackage[fleqn]{amsmath}
\usepackage{amssymb}
\usepackage{makeidx}  % allows for indexgeneration
\usepackage{subfig}  % allows for indexgeneration
\usepackage{color}  % allows for indexgeneration
\usepackage{url}
\usepackage{hyperref}
\usepackage{float}
\usepackage{mathtools}
\usepackage{acronym}
\usepackage{pgfgantt}
\usepackage{adjustbox}
\usepackage{rotating}
\usepackage[graphicx]{realboxes}
\definecolor{fade}{rgb}{0.8,0.8,0.8}

\newacro{AES}{Advanced Encryption Standard}
\newacro{API}{Application Programming Interface}
\newacro{BOSH}{Bidirectional-streams Over Synchronous HTTP}
\newacro{CBC}{Cipher Block Chaining}
\newacro{CPU}{Central Processing Unit}
\newacro{CRUD}{Create, Read, Update and Delete}
\newacro{CSS}{Cascading Style Sheets}
\newacro{DOM}{Document Object Model}
\newacro{DTLS}{Datagram Transport Layer Security}
\newacro{FMS}{Flash Media Server}
\newacro{HTML}{HyperText Markup Language}
\newacro{HTTP}{Hypertext Transfer Protocol}
\newacro{ICE}{Interactive Connectivity Establishment}
\newacro{IPv4}{Internet Protocol Version 4}
\newacro{IPv6}{Internet Protocol Version 6}
\newacro{IP}{Internet Protocol}
\newacro{JSON}{JavaScript Object Notation}
\newacro{MPEG}{Moving Picture Experts Group}
\newacro{NAT}{Network Address Translation}
\newacro{OT}{Operational transformation}
\newacro{P2P}{Peer-to-peer}
\newacro{PSTN}{Public Switched Telephone Network}
\newacro{RFC}{Request For Comments}
\newacro{RTCP}{Real Time Control Protocol}
\newacro{RTMFP}{Real-Time Media Flow Protocol}
\newacro{RTMP}{Real Time Messaging Protocol}
\newacro{RTP}{Real-time Transport Protocol}
\newacro{SAMI}{Synchronized Accessible Media Interchange}
\newacro{SCTP}{Stream Control Transmission Protocol}
\newacro{SDP}{Session Description Protocol}
\newacro{SigOfly}{Signaling-On-the-fly}
\newacro{SIMPLE}{SIP for Instant Messaging and Presence Leveraging Extensions}
\newacro{SIP}{Session Initiation Protocol}
\newacro{SMIL}{Synchronized Multimedia Integration Language}
\newacro{SMS}{Short Message Service}
\newacro{SRTCP}{Secure RTCP}
\newacro{SRTP}{Secure Real-time Transport Protocol}
\newacro{SRT}{SubRip Text}
\newacro{SSL}{Secure Sockets Layer}
\newacro{STUN}{Session Traversal Utilities for NAT}
\newacro{SVG}{Scalable Vector Graphics}
\newacro{TCP}{Transmission Control Protocol}
\newacro{TLS}{Transport Layer Security}
\newacro{TMN}{This Means Nothing}
\newacro{TURN}{Traversal Using Relays around NAT}
\newacro{UDP}{User Datagram Protocol}
\newacro{VoIP}{Voice Over IP}
\newacro{WebRTC}{Web Real-Time Communication}
\newacro{WebVTT}{Web Video Text Tracks}
\newacro{XAML}{eXtensible Application Markup Language}
\newacro{XEP}{XMPP Extensions}
\newacro{XHTML}{eXtensible Hypertext Markup Language}
\newacro{XML}{eXtensible Markup Language}
\newacro{XMPP}{Extensible Messaging and Presence Protocol}

%\overfullrule=2cm

\newganttchartelement*{mymilestone}{
mymilestone/.style={
shape=isosceles triangle,
inner sep=0pt,
draw=cyan,
top color=white,
bottom color=cyan!50
},
mymilestone incomplete/.style={
/pgfgantt/mymilestone,
draw=yellow,
bottom color=yellow!50
},
mymilestone label font=\slshape,
mymilestone left shift=0pt,
mymilestone right shift=0pt
}

\newgantttimeslotformat{stardate}{%
\def\decomposestardate##1.##2\relax{%
\def\stardateyear{##1}\def\stardateday{##2}%
}%
\decomposestardate#1\relax%
\pgfcalendardatetojulian{\stardateyear-01-01}{#2}%
\advance#2 by-1\relax%
\advance#2 by\stardateday\relax%
}

@@

\begin{abstract}

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

Sed ut perspiciatis unde omnis iste natus error sit voluptatem accusantium doloremque laudantium, totam rem aperiam, eaque ipsa quae ab illo inventore veritatis et quasi architecto beatae vitae dicta sunt explicabo. Nemo enim ipsam voluptatem quia voluptas sit aspernatur aut odit aut fugit, sed quia consequuntur magni dolores eos qui ratione voluptatem sequi nesciunt.

\keywords{keyworkd1, keyworkd2, keyworkd3}
\end{abstract}

\section{Introduction}
  \input{intro.tex}

\section{Related Work}
  \input{state01.tex}
  \input{state02.tex}
  \input{state03.tex}
  \input{state04.tex}

\section{Proposed Architecture} % English
  \input{arch01.tex}

\section{Methodology} % Section

		\input{method.tex}

	\subsection{Planned Schedule} % English
		\input{schd01.tex}

\section{Conclusions} % English

\subsection{Summary} % English
Neste secção deve-se fazer o resumo do trabalho efectuado, retomando a ideia, as contribuições definidas e a forma como estas se materializaram

\subsection{Conclusions} % English
Nesta secção devem ser retiradas conclusões do trabalho realizado, em face dos resultados obtidos \cite{exemplo}.

\bibliographystyle{splncs03}
\bibliography{references}
